### 2020-05-29 paper.tex
Add Results

We planned to have a one hour session for the actual experiment with each subject, followed-up by a short, unattended after-action survey. The experiment was executed in two consecutive blocks of 25 minutes each. We provided a ZIP file containing the source code for two frontend web applications implemented using TypeScript and RxJS along with a test suite at the start of the experiment. Each of these applications were rigged with two to three bugs which we asked the subjects to identify and fix using whatever debugging techniques they prefer and commonly use. A block was considered as complete once either the test suite signaled all bugs as resolved or the 25 minutes were exceeded. We asked our subjects to act like in a pair programming situation where they ``think out loud'' their thought process. We refrained to answer any question related to the ``where'' a bug has to be expected though.

@@

We decided to monitor our subjects progress remotely using voice chat and screen sharing due to the COVID-19 situation at the time of our study. This allowed us to record the sessions with relative low technical effort for later evaluation.

The quantitative after-action survey provided after the main part of the study was provided within 24 hours after a subjects participation. We asked the subjects about (i) the number of years they have experience with RxJS, (ii) if they currently use RxJS on or off their jobs, (iii) in which field (like frontend, backend or others) they use RxJS and finally (iv) which tools and techniques they use to debug RxJS-based code.

\subsection{Study Results}

>>>>

We planned to have a one hour session for the actual experiment with each subject, followed-up by an unattended quantitative after-action survey. The experiment was executed in two consecutive blocks of 25 minutes each. We provided a ZIP file containing the source code for two frontend web applications implemented using TypeScript and RxJS along with a test suite at the start of the experiment. Each of these applications were rigged with two to three bugs which we asked the subjects to identify and fix using whatever debugging techniques they prefer and commonly use. A block was considered as complete once either the test suite signaled all bugs as resolved or the 25 minutes were exceeded. We asked our subjects to act like in a pair programming situation where they ``think out loud'' their thought process. We refrained to answer any question related to the ``where'' a bug has to be expected though.

@@

We decided to monitor our subjects progress remotely using voice chat and screen sharing due to the COVID-19 situation at the time of our study. This allowed us further to record the sessions with relative low technical effort for later evaluation.

The after-action survey was provided within 24 hours after a subjects participation in the main part of the study. We asked the subjects about (i) the number of years they have experience with RxJS, (ii) if they currently use RxJS on or off their jobs, (iii) in which field (like frontend, backend or others) they use RxJS and finally (iv) which tools and techniques they use to debug RxJS-based code. The respective answers allowed us to put the observed actions into perspective and detect potential irregularities in case a subject acted differently as they would have in a ``real'' situation.

\subsection{Results}

After the subjects got a feel for what the application on front of them should do, all of them used the provided test suite to check what features do not work as expected and tried to recreate the failing behavior in the UI manually. Two of them used the traditional debugging tools provided by their browser or IDE to step through parts of the code trying to understand what triggered the failing tests.

For both problems given, all subjects could be observed to make use of manually added trace log statements which they either added to existing arrow functions and/or using the \mintinline{TypeScript}{tap} operator. Neither did any of them use additional external tools where they put parts of the code for further inspection nor did they install additional debugging libraries like rxjs-spy.
After the 25 minutes of the second block exceeded, one subject noted that they would have usually started now to decompose the problem into smaller pieces and observe their behavior more isolated.

The responses on the survey showed that 75\% of the subject population had two or more years of experience with RxJS. Where all of them use RxJS to develop frontend applications, one subject declared having RxJS used for backend development as well. When asked what tools they usually use for debugging, only one subject told not to use the traditional debugger of their browser and/or IDE. Two of them leverage additional tracing functionality of rxjs-spy and all of them use manual log statements.

\subsection{Interpretation}
